Index measures for oak decline severity using phenotypic descriptors

### 2021-01-05 manuscript/manuscript.Rmd
elsartical-harv natbib citation style now used for reference format

---
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linespread{2}
  - \linenumbers
bibliography: references.bib
csl: forest-ecology-and-management.csl
---

@@

By defining decline severity objectively across a spectrum, these decline indexes provide greatly enhanced sensitivity over previous categorical decline status assignments.
This approach could enhance integration with large scale data such as those from genome wide association studies or remote sensing [@stocks2019; @evans2012]. These index measures allow sensitive comparisons of visual health to be made for the same tree between years as well as comparisons of trees between different locations.

>>>>

---
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
    citation_package: natbib
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linespread{2}
  - \linenumbers
bibliography: references.bib
biblio-style: elsarticle-harv
# csl: forest-ecology-and-management.csl
---

@@

By defining decline severity objectively across a spectrum, these decline indexes provide greatly enhanced sensitivity over previous categorical decline status assignments.
This approach could enhance integration with large scale data such as those from genome wide association studies or for providing ground-truth data for remote sensing [@stocks2019; @evans2012]. These index measures allow sensitive comparisons of visual health to be made for the same tree between years as well as comparisons of trees between different locations.
